%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage[usenames,dvipsnames]{color} % Required for custom colors
\usepackage{graphicx} % Required to insert images
\usepackage{listings} % Required for insertion of code
\usepackage{courier} % Required for the courier font
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\newcommand{\writer}{Davide Peron}

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1} % Line spacing

% Set up the header and footer
\pagestyle{fancy}
\lhead{\writer} % Top left head
\chead{Case: Rhino-1151910} % Top center head
\rhead{\today} % Top right header
\lfoot{Signature: } % Bottom left footer
\cfoot{} % Bottom center footer
\rfoot{Page\ \thepage\ of\ \protect\pageref{LastPage}} % Bottom right footer
\renewcommand\headrulewidth{0.4pt} % Size of the header rule
\renewcommand\footrulewidth{0pt} % Size of the footer rule

\fancypagestyle{plain}{
	\fancyfoot[C]{}
}


\setlength\parindent{0pt} % Removes all indentation from paragraphs

\setcounter{secnumdepth}{0} % Removes default section numbers

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title{
	\textmd{\textbf{EXPERT WITNESS REPORT}}\\
	\vspace{0.3in}
	\textsc{\Large IN RELATION TO}\\
	\vspace{0.3in}
	\textmd{\textbf{ILLEGAL RHINOCEROS IMAGES}}\\
	\vspace{0.7in}
	\textmd{\Large \textbf{BY REQUEST OF: }}
	\textsc{\Large Mr. Gareth Davies}\\
	\vspace{0.1in}
	\textmd{\Large \textbf{NAME OF EXPERT: }}
	\textsc{\Large \writer}\\
	\vspace{0.1in}
	\textmd{\Large \textbf{CASE NAME: }}
	\textsc{\Large Rhino-1151910}
	\date{}
}

%----------------------------------------------------------------------------------------

\begin{document}

\parbox{0.4\textwidth}{
	\normalsize
	\textbf{UK Statues and Guidelines Followed:\\
	Criminal Procedure Rules, r 27.1 (1)\\
	Criminal Justice Act 1967, s. 9\\
	Magistrates’ Court Act 1980, s.5B\\
	ACPO Digital Evidence Guidelines}
}

\vspace{0.5in}

{\let\newpage\relax\maketitle}

\centering
\parbox{0.7\textwidth}{
	This statement (consisting of \protect\pageref{LastPage}
	pages each signed by myself) is true to the best of
	my knowledge and belief and I make it knowing that, if tendered in evidence, I shall
	be liable to prosecution if I have wilfully stated in it anything which I know to be false
	or do not believe to be true.
}

\parbox{0.7\textwidth}{
	\vspace{0.2in}
	Signature: \hspace{2in} Date:
}
%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS
%----------------------------------------------------------------------------------------

%\setcounter{tocdepth}{1} % Uncomment this line if you don't want subsections listed in the ToC

\newpage
\tableofcontents
\newpage

\section{Curriculum Vitae}

I am \writer ~and I am a student in MSc Telecommunications Engineering in University of Padova. I have a Bachelor Degree in Information Engineering.
I have matured my skills in digital devices and networks analysis during my academic career and now I can analyse in depth some devices like smartphones, hard disks, live computer or computer networks.

\vspace{0.3in}

\begin{tabular}{l l}
	\textbf{Name} & \writer\\
	\textbf{Enrolment Number} & 1151910\\
	\textbf{Institutional E-mail} & davide.peron.2@studenti.unipd.it\\
	\textbf{Occupation} & Student in first year of Telecommunications Engineering
\end{tabular}

\section{Instruction/Objectives}

\subsection{Abstract of the case}

The city of New Orleans passed a law in 2004 making possession of nine or more unique rhinoceros images a serious crime. The network  administrator at the University of New Orleans recently alerted police when some illegal rhino traffic was flagged by his network monitoring software. The suspect is a research student and is the primary user of a University computer. The computer hard drive was missing at the time of the alleged offence.

Police have taken a forensically image of USB flash drive seized from one of the University's computer.
Network administrator has recovered three network traces involve the machine with the missing hard drive.

\subsection{Statement of Instructions}
The police has requested that I \writer ~carry out an investigation on the following evidence items:

\begin{itemize}
	\item \textit{RHINOUSB.dd} USB Image
	\item Three network traces
\end{itemize}

The purpose of this report is to outline the result of the investigation in order to answer to the question \textit{Is there any evidence to show that the suspect did store illegal images on the University computer?}

\section{Received Evidence Items}

For each evidence item received, the correspondent MD5 hash checksum was provided.
This checksum is recalculated at the end of the investigation to ensure the integrity of evidence items.

The provided MD5 checksums are shown in \autoref{tab:checksum}

\begin{table}[h!]
	\centering
	\begin{tabular}{l|l}
		Evidence Item & MD5 checksum\\
		\hline
		RHINOUSB.dd & 80348c58eec4c328ef1f7709adc56a54\\
		rhino.log & c0d0093eb1664cd7b73f3a5225ae3f30\\
		rhino2.log & cd21eaf4acfb50f71ffff857d7968341\\
		rhino3.log & 7e29f9d67346df25faaf18efcd95fc30
	\end{tabular}
	\caption{Evidence Items's MD5 checksums}
	\label{tab:checksum}
\end{table}

\end{document}
